### 2010-06-02 doc/manuals/configuration/configuration_manual.tex
Adding description of new Logger features - Domain and Reopen

Logging options should be specified under the \texttt{Logger} element under the
\texttt{Server} element. The \texttt{File} element specifies which file to write
log messages to and if not present log messages will be written to the
\texttt{/var/log/arched.log} file. Each log message is associated with a log
level which indicates the serverity of the message. The following log levels
exist in WS-ARC, ordered by serverity: \texttt{FATAL}, \texttt{ERROR},
\texttt{WARNING}, \texttt{INFO}, \texttt{VERBOSE} and \texttt{DEBUG}. With
the \texttt{Level} element the level of messages being reported can be
specified. Log messages with a higher or same level as specified by the
\texttt{Level} element will be written to the log file. The default log level is
\texttt{WARNING}. \newline
By default the log file is not limited in size, neither
will any log rotation be done. The \texttt{Maxsize} and \texttt{Backups}
elements can be used to change this behaviour. The \texttt{Maxsize} element sets
the maximum file size of the log file in bytes, while the \texttt{Backups}
element specifies the number of files used for log rotation. When the size of
the log file exceeds the limit specified by the \texttt{Maxsize} element the log
file is renamed to \texttt{<log-file>.1}. If this file exist it is renamed to
\texttt{<log-file>.2} and so forth up to the number specified by
\texttt{Backups}, which means that the last file will be deleted. The log file
size is only allowed to exceed the specified limit by the size of one log
message. If the \texttt{Maxsize} element have been specified and no
\texttt{Backups} element is specified then log rotation will not be carried out,
thus the log file is truncated when the limit is exceeded.

@@

The following example show the use of the above configuration options:
\begin{lstlisting}[language=xml]
<?xml version="1.0"?>
<ArcConfig>
  <Server>
    <PidFile>/tmp/arched.pid</PidFile>
    <User></User>
    <Group></Group>
    <Logger>
      <File>/tmp/arched.log</File>
      <Level>WARNING</Level>
      <MaxSize>1000000</MaxSize>
      <Backups>5</Backups>
    </Logger>
  </Server>
  <ModuleManager>
    <Path>/usr/lib/arc</Path>
  </ModuleManager>
  <Plugins>
    <Name>plugin1</Name>
    <Name>plugin2</Name>
    ...
  </Plugins>
  ...
</ArcConfig>
\end{lstlisting}

>>>>

Logging options should be specified under the \texttt{Logger} element under the
\texttt{Server} element. The \texttt{File} element specifies which file to write
log messages to and if not present log messages will be written to the
\texttt{/var/log/arched.log} file. Each log message is associated with a log
level which indicates the serverity of the message. The following log levels
exist in WS-ARC, ordered by serverity: \texttt{FATAL}, \texttt{ERROR},
\texttt{WARNING}, \texttt{INFO}, \texttt{VERBOSE} and \texttt{DEBUG}. With
the \texttt{Level} element the level of messages being reported can be
specified. Log messages with a higher or same level as specified by the
\texttt{Level} element will be written to the log file. The default log level is
\texttt{WARNING}.

The log messages are also assigned different domains. Domain is a string
indicating where message came from. Domains follow hierarchical layout with
top level called \texttt{Arc} and subdomains added to it separated by dot -
like \texttt{Arc.MCC.TCP}. It is possible to assign different logging levels
to different domains by using multiple \texttt{Level} elemets each with
\texttt{Domain} attribute containing affected domain name. The \texttt{Level}
without \texttt{Domain} is assigned to \texttt{Arc} domain and is inherited
by all other domains unless they have theirs levels specified explicitely.

By default the log file is not limited in size, neither
will any log rotation be done. The \texttt{Maxsize} and \texttt{Backups}
elements can be used to change this behaviour. The \texttt{Maxsize} element sets
the maximum file size of the log file in bytes, while the \texttt{Backups}
element specifies the number of files used for log rotation. When the size of
the log file exceeds the limit specified by the \texttt{Maxsize} element the log
file is renamed to \texttt{<log-file>.1}. If this file exist it is renamed to
\texttt{<log-file>.2} and so forth up to the number specified by
\texttt{Backups}, which means that the last file will be deleted. The log file
size is only allowed to exceed the specified limit by the size of one log
message. If the \texttt{Maxsize} element have been specified and no
\texttt{Backups} element is specified then log rotation will not be carried out,
thus the log file is truncated when the limit is exceeded.

By default log file is kept continiously open. For compatibility with external
log rotating utilities it is possible to force log file being closed after
every log record is written and re-opened for new one. For that optional
\texttt{Reopen} element is used. If set to \texttt{true} it turns compatibility
mode on.

@@

The following example show the use of the above configuration options:
\begin{lstlisting}[language=xml]
<?xml version="1.0"?>
<ArcConfig>
  <Server>
    <PidFile>/tmp/arched.pid</PidFile>
    <User></User>
    <Group></Group>
    <Logger>
      <File>/tmp/arched.log</File>
      <Level>WARNING</Level>
      <Level Domain="Arc.MCC.TCP">DEBUG</Level>
      <MaxSize>1000000</MaxSize>
      <Backups>5</Backups>
      <Reopen>false</Reopen>
    </Logger>
  </Server>
  <ModuleManager>
    <Path>/usr/lib/arc</Path>
  </ModuleManager>
  <Plugins>
    <Name>plugin1</Name>
    <Name>plugin2</Name>
    ...
  </Plugins>
  ...
</ArcConfig>
\end{lstlisting}
